Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
it seems we didn't put LR and MLP in final result

\fixme{how the data is represented}

\fixme{is program pair the correct term?}

@@

For decision tree and random forest, we use the implementation from
\textsc{scikit-learn}~\cite{scikit-learn}.
% Due to the large amount of data points, we did not use \textsc{scikit-learn}'s
% implementation for logistic regression and multilayer perceptron.
% We implementation both model using
% \textsc{keras}~\cite{chollet2015keras} with mini-batch gradient descent.

@@

\emph{Hyper-parameters}
All hyper-parameters are tuned using three-fold cross-validation on the
intended score (Top-$k$ accuracy).
For RF, the maximum depth of each tree is searched from $25$ to $35$ and the
number of tree are fixed to $500$.
For decision tree maximum depth of the tree is searched from $25$ to $35$ with interval of $5$,
the minimum impurity decrease for each split is searched from $10^{-7}$ to
$10^{-3}$ with multiple of $10^{-2}$ and the minimum samples in each leaf is set to $200$.
For logistic regression and MLP, binary cross-entropy is set as the loss
function and Adam \cite{kingma2014adam} optimizer is used.
Learning rate is set to $0.1$ and the number of epochs are $10$.
L2 regularization is applied to the weights of both models,
the weight for L2 term is searched from $10^0$ to $10^{-5}$ with a multiple of $10^{-1}$.
Other parameters that are not mentioned are kept with the default setting of the
original packages.

>>>>

@@

For decision tree and random forest, we use the implementation from
\textsc{scikit-learn}~\cite{scikit-learn}.
%Due to the size of the dataset, we did not use \textsc{scikit-learn}'s
%implementation for logistic regression and MLP.
%We implementation both model using
%\textsc{keras}~\cite{chollet2015keras} with mini-batch gradient descent.

@@

\emph{Hyper-parameters}
All hyper-parameters are tuned using three-fold cross-validation on the
intended score (Top-$k$ accuracy).
For RF, the maximum depth of each tree is searched from $25$ to $35$ and the
number of tree are fixed to $500$.
For decision tree maximum depth of the tree is searched from $25$ to $35$ with interval of $5$,
the minimum impurity decrease for each split is searched from $10^{-7}$ to
$10^{-3}$ with multiple of $10^{-2}$ and the minimum samples in each leaf is set to $200$.
%For logistic regression and MLP, binary cross-entropy is set as the loss
%function and Adam \cite{kingma2014adam} optimizer is used.
%Learning rate is set to $0.1$ and the number of epochs are $10$.
%L2 regularization is applied to the weights of both models,
%the weight for L2 term is searched from $10^0$ to $10^{-5}$ with a multiple of $10^{-1}$.
Other parameters that are not mentioned are kept with the default setting of the
original packages.
